\chapter{mclogd}

\section{Receiving log messages on the looopback address}
\textit{mclogd} can accept unencrypted log messages on the loopback
address (\texttt{127.0.0.1} and/or \texttt{::1}).  This is how it
receives log messages from applications on the local host.

\section{Receiving log messages via multicast}
\textit{mclogd} can receive encrypted log messages via multicast.
This is how \textit{mclogd} receives log messages from instances of
\textit{mclogd} running on other hosts.  Note that in order to
decrypt these messages, \textit{mclogd} must request the decryption
key from each multicast source, and in the process must prove
identity via signature using \texttt{Credence} and must be known by
the remote \textit{mclogd} instance.

\section{Sending log messages via multicast}
\textit{mclogd} can send encrypted log messages via multicast.
This is how \textit{mclogd} sends log messages to instances of
\textit{mclogd} on other hosts.  Receivers must request the decryption
key from a given instance of \textit{mclogd}, and must prove they
are a trusted identity via signature using \texttt{Credence}.

\section{Saving log messages to files}
\textit{mclogd} saves log messages received via the loopback
and multicast to local files.  Filters may be used to select
which messages are saved to a given log file path.  Log file
paths may use message contents in their construction:
\texttt{\%H} will be replaced with the source hostname,
\texttt{\%I} will be replaced with the application identifier
(program name), and \texttt{\%F} will be replaced with the
log facility (\texttt{daemon}, \texttt{user}, \texttt{local0},
et. al.).
